\begin{thebibliography}{99}
\bibitem{ocdma1} H.M. Kwon, "Optical Orthogonal Code-division Multiple-access 
system -- Part I: APD Noise and Thermal Noise," IEEE Trans. Communications,
vol.42, no.7, pp.2470--2479, July 1994. 
%
\bibitem{ocdma2} Y. Qiu, S. Chen, H.H. Chen, W. Meng, 
"Visible Light Communication based on CDMA Technology," IEEE Wireless Communications, 
vol.25, no.2, pp.178--185, Apr. 2018.
%
\bibitem{ocdma3} M.Y. Liu, T.L. Wang, S.M. Tseng, 
"Throughput Performance Analysis of Ascynchronous Optical CDMA Networks 
with Channel Load Sensing Protocol," IEEE Photonics Journal, 
vol.9, no.3, June 2017.
%
\bibitem{ocdma4} S.H. Chen, C.W. Chow, 
"Color-shift Keying Code-division Multiple-access Transmission for 
RGB-LED Visible Light Communications using Mobile Phone Camera," 
IEEE Photonics Journal, vol.7, no.6., Dec. 2014. 
%
\bibitem{ocdma5} K. Kiasaleh, 
"Performance of APD-based, PPM Free-space Optical Communication Systems in Atmospheric Turbulence," 
IEEE Trans. Communications, vol.53, no.9, pp.1455--1461, Sept. 2005. 
%
\bibitem{scinti} X. Zhu, J.M. Kahn, 
"Free-space Optical Comuunication through Atmospheric Turbulence Channels," 
IEEE Trans. Communications, vol.50, no.8, pp.1293--1300, Aug. 2002.
%
%
\bibitem{ocdma6} M. Hadi, M.R. Pakravan, 
"Analysis and Design of Adaptive OCDMA Passive Optical Networks," 
Journal of Lightwave Technology, vol.35, no.14, pp.2853--2863, 2017. 
%
\bibitem{ook} J. Li, M. Uysal,  
"Optical Wireless Communications: System Model, Capacity and Coding," 
Proc. IEEE VTC, vol.1, pp.168--172, Oct. 2003. 
%
\bibitem{sik1} T. Yamashita, M. Hanawa, Y. Tanaka, M. Takahara, 
"An Optical Code Division Multiplexing System using Hadamard Codes and SIK," 
IEICE Technical Report, OCS98-1, May 1998. 
%
\bibitem{sik2} Y. Kozawa, H. Habuchi, 
"Theoretical Ananlysis of Atomospheric Optical DS/SS with On-off Orthogonal 
M-sequence Pairs," Proc. ICICS, P0686, Dec. 2007. 
%
\bibitem{csk1} N. Ochiai, S. Kushibiki, T. Matsushima, Y. Teramachi, 
"Performance Analysis of Synchronous Optical CDMA System with EWO signaling," 
IEICE Trans. Fundamentals, vol.J86-A, no.9, pp957--968, Sept. 2003. 
%
%
\bibitem{csk} C-P. Hsieh, C-Y. Chang, G-C. Yang, W.C. Kwong, 
"A Bipolar-bipoloar Code for Asynchronous Wevelength-time Optical CDMA," 
IEEE Trans. Communications, vol.54, no.7, pp.2572--2578, July 2006. 
%
\bibitem{csk2} S. Takayanagi, H. Habuchi, Y. Kozawa, 
"Optical-wireless Enhanced Code-shift-keyging with IM/DD," 
Proc. APCC, 14-PM1-C, Oct. 2015.
\end{thebibliography}

